---
title: "A Quick Introduction to alma"
author: "Otho Mantegazza"
date: "`r Sys.Date()`"
output:
  knitr:::html_vignette:
    toc: yes
    number_sections: true
vignette: >
  %\VignetteIndexEntry{Introduction to alma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

**Alma** stands for **Alignment Markup** and is a small utility to format protein sequence aligment in HTML. 

Alma has been build exclusively to be used within Rmarkdown files, so that `Biostrings` elements can be nicely printed when we render Rmarkdown into HTML.

# Load example file

```{r}
aa_file <- system.file("exdata/REM_example.fasta", package = "alma")
aa_set <- Biostrings::readAAStringSet(filepath = aa_file)

```

Generally we like that protein sequences are printed using colour code to identify aminoacid, Biostrings, being build to be used within R, does not perform that.

```{r}
print(aa_set)
```

# Temporary section - how to display HTML from code?

```{r}
cat("<pre><SPAN style=\"color:#33cc00\">I</SPAN></pre>")
print("<SPAN>I</SPAN>")
```

```{r, results='asis'}
# knitr::asis_output(cat("<pre><SPAN style=\"color:#33cc00\">I</SPAN></pre>"))
cat("<pre><SPAN style=\"color:#33cc00\">I</SPAN></pre>")
```

# print amino acids

```{r, results='asis'}
cat(aa2html(aa_set = aa_set))
```





